\documentclass[11pt, letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}

\title{\vspace{-2em}Lab 7: Team Reproducibility Report}
\author{Tony Nguyen \and Daniel Evans \and Joel Vinas}
\date{}

\begin{document}
\maketitle
\vspace{-3em}

\begin{center}
\textbf{Project Repository:} \url{https://github.com/mosomo82/ReMindRAG_Week7}
\end{center}

\section*{Division of Responsibilities}
Our team successfully executed Lab 7 by dividing the workload into three distinct, non-overlapping phases, allowing for parallel execution and individual accountability.

\subsection*{Project Component Ownership \& Division of Labor Summary}
To ensure rapid iteration and clear accountability, we mapped our division of labor directly to the core architectural components of the codebase:

\vspace{1em}
\noindent\begin{tabular}{|p{0.25\linewidth}|p{0.15\linewidth}|p{0.5\linewidth}|}
\hline
\textbf{Project Component} & \textbf{Primary Owner} & \textbf{Description of Responsibilities} \\
\hline
\textbf{Environment \& Infrastructure} & Tony Nguyen & Authored \texttt{Makefile}, \texttt{reproduce.sh/ps1}, Dockerfile, \texttt{.env.template}, and test suite (\texttt{test\_reproducibility.py}); fixed PyTorch/NLTK dependency bugs and Streamlit Cloud deployments. \\
\hline
\textbf{Evaluation Metrics \& Testing} & Daniel Evans & Built \texttt{tests/smoke\_test.py}, integrated quantitative metrics (ROUGE, BLEU, BERTScore), and designed entity faithfulness scoring templates. \\
\hline
\textbf{AI Agents \& Cost Control} & Joel Vinas & Audited LLM orchestration (\texttt{eval\_LooGLE.py}), integrated dynamic judge model selection (e.g., \texttt{gpt-4o-mini}), applied global graph deterministic seeds, and designed CoT injection points. \\
\hline
\end{tabular}
\vspace{1em}


\subsection*{Tony Nguyen — Related Work Reproduction \& Core Pipeline Audit}
\textbf{Primary Ownership:} ReMindRAG Reproduction and Environmental Architecture
\begin{itemize}[leftmargin=*]
    \setlength{\itemsep}{1pt}
    \item \textbf{Repo Selection \& Setup:} Selected ReMindRAG as the related work, cloned the repository, and audited the initial environment.
    \item \textbf{Dependency Management:} Identified and fixed critical containerization blockers (e.g., missing CUDA package URLs, UTF-16 encoding errors in \texttt{requirements.txt}).
    \item \textbf{Reproducibility Auditing:} Authored the \texttt{REPRO\_AUDIT.md} document, logging 17 distinct reproducibility failures categorized by severity.
    \item \textbf{Automation:} Developed the \texttt{reproduce.sh} script (Linux/macOS) and \texttt{reproduce.ps1} (Windows/PowerShell) to allow single-command execution of the RAG pipeline.
    \item \textbf{Dockerization \& Cloud Deployment:} Created a multi-stage Dockerfile and debugged Streamlit Cloud deployment failures by resolving PyTorch PyPI wheel conflicts (\texttt{+cu126}).
    \item \textbf{Dependency Auditing:} Fixed a hidden tokenizer crash where NLTK failed to chunk Markdown tables, and mapped missing architectural dependencies (\texttt{einops} for Nomic MoE).
\end{itemize}

\subsection*{Daniel Evans — Evaluation Metrics \& Baseline Implementation}
\textbf{Primary Ownership:} Quantitative Benchmarking
\begin{itemize}[leftmargin=*]
    \setlength{\itemsep}{1pt}
    \item \textbf{Metric Expansion:} Designed the implementation plan to replace binary pass/fail RAG validation with robust quantitative metrics (ROUGE-L, BLEU, BERTScore).
    \item \textbf{Testing Infrastructure:} Developed the \texttt{smoke\_test.py} script to validate end-to-end traversal without requiring API keys.
    \item \textbf{Faithfulness Scoring:} Prototyped the prompt template required to verify that extracted knowledge graph entities are factually grounded in the source text.
\end{itemize}

\subsection*{Joel Vinas — Advanced Prompting \& Quality Enhancements}
\textbf{Primary Ownership:} LLM Reasoning and System Robustness
\begin{itemize}[leftmargin=*]
    \setlength{\itemsep}{1pt}
    \item \textbf{Reasoning Injection:} Designed the upgrade path for implementing Chain-of-Thought (CoT) and Self-Consistency methodologies into the entity extraction agent.
    \item \textbf{Cost Control:} Refactored the evaluation orchestrator (\texttt{eval\_LooGLE.py}) to allow dynamic switching of the judge model (e.g., overriding hardcoded \texttt{gpt-4o} with \texttt{gpt-4o-mini}).
    \item \textbf{System Improvements:} Integrated the \texttt{--seed} parameter globally to enforce strict deterministic randomness across all PyTorch and NumPy operations.
\end{itemize}

\end{document}
